---
title: "607 Week 3 Project 1"
author: "Peter Kowalchuk"
date: "9/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Project 1

###In this project, you're given a text file with chess tournament results where the information has some structure. Your job is to create an R Markdown file that generates a .CSV file (that could for example be imported into a SQL database) with the following information for all of the players:   

###Player's Name, Player's State, Total Number of Points, Player's Pre-Rating, and Average Pre Chess Rating of Opponents  

To solve this project we start by building vectors for each one of the variables requireded from each player. We then combine the vectors into a data frame and export it to a csv file. We need to build 5 vectors, one for each variable. Each of these Vectors will have a total of 64 elements, one for each player. These elements represent the rows in out final data frame and csv file.

##Import tournament data

```{r}
library(stringr)

tournament<-readLines("tournamentinfo.txt")
tournament
```


##Player Names

```{r}
playerNames<-str_extract(str_extract(tournament,"\\| [A-Z]+[:print:]+[A-Z]+     "),"[A-Z]+[:print:]+[A-Z]+")
playerNames<-playerNames[!is.na(playerNames)]
playerNames
```

##Player States

```{r}
playerStates<-str_extract(str_extract(tournament,"  [A-Z][A-Z] \\|"),"[A-Z][A-Z]")
playerStates<-playerStates[!is.na(playerStates)]
playerStates
```

##Total Number of Points

```{r}
totalPoints<-str_extract(str_extract(tournament,"\\|[0-9].[0-9]"),"[0-9].[0-9]")
totalPoints<-totalPoints[!is.na(totalPoints)]
totalPoints
```

##Player's Pre-Rating

```{r}
playerPreRating<-str_extract(str_extract(tournament,"R: +[:digit:]+"),"[:digit:]+")
playerPreRating<-playerPreRating[!is.na(playerPreRating)]
playerPreRating
```

##Average Pre Chess Rating of Opponents

```{r}
opponents<-str_extract_all(tournament,"\\|[0-9]\\.[0-9] +\\|[A-Z] +[0-9]*\\|[A-Z] +[0-9]*\\|[A-Z] +[0-9]*\\|[A-Z] +[0-9]*\\|[A-Z] +[0-9]*\\|[A-Z] +[0-9]*\\|[A-Z] +[0-9]*\\|")
opponents<-Filter(length,opponents)
opponents<-str_extract_all(opponents,"\\|[A-Z] +[0-9]*\\|[A-Z] +[0-9]*\\|[A-Z] +[0-9]*\\|[A-Z] +[0-9]*\\|[A-Z] +[0-9]*\\|[A-Z] +[0-9]*\\|[A-Z] +[0-9]*\\|")
opponents<-str_extract_all(opponents,"[L,W,D] +[0-9]*")
opponents<-str_extract_all(opponents,"[0-9]?[0-9]")
opponents
j<-0
i<-0
avgPreRatingOpp<- vector(mode="numeric", length=0)
for (a in opponents) {
  j=j+1
  print(paste0("Player Number: ",j))
  avgPreRatingOpp[j]<-0
  i<-0
  for (b in opponents[[j]]) {
    i<-i+1
    avgPreRatingOpp[j]<-avgPreRatingOpp[j]+as.numeric(playerPreRating[as.numeric(b)])
    #print(avgPreRatingOpp[j])
  }
  avgPreRatingOpp[j]<-round(avgPreRatingOpp[j]/i,0)
  print(avgPreRatingOpp[j])
}
avgPreRatingOpp
```

##Build data frame

```{r}
final<-data.frame(playerNames,playerStates,totalPoints,playerPreRating,avgPreRatingOpp)
colnames(final)<-c("Player Name","Player State","Total Number of Points","Player's Pre-Rating","Average Pre Chess Rating of Opponents")
final
```

##Export to CSV file

```{r}
write.csv(final,"ChessPlayersReport.csv")
```

